ESRC SDAI Application

### 2019-06-19 case_for_support.tex
Anna update

\textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
In our last research project, we will be using the CSEW and WMP datasets to investigate the environmental predictors of domestic abuse. First, using data from the CSEW, we will be looking at the association between neighbourhood-level characteristics and the prevalence of domestic abuse as well the decision to report, and we will complement this with an additional analysis on WMP and census data. Previous literature has suggested various pathways of how neighbourhood characteristics affect domestic abuse, and our rich data allows us to determine the relative explanatory power of these. Understanding how neighbourhood-level characteristics affect the prevalence of domestic abuse and reporting behaviour is crucial for the most effective distribution of resources to help victims and targeted awareness campaigns. Second, we will be looking at how time-varying factors affect domestic abuse.

\textcolor{red}{\textit{What we know so far}}  neighbourhood-level predictors of domestic abuse: social disorganization theory (socio-economic disadvantage and residential instability disrupt social bonds a limit collective ability to maintain control and recognise IPV); cultural norms through social learning process (high IPV neighbourhoods where people observe influential others being rewarded for engaging in IPV, whereas in low IPV neighbourhoods perpetrators get socially ostracized); women's empowerment reduces IPV;  abuser's lack of employment and alcohol consumption can be a risk factor; alcohol outlet density; churches, playgrounds, community networks;  however, in deprived neighbourhoods where IPV is accepted social interactions can increase IPV

>>>>

\textcolor{red}{\textit{Short intro about aims, highlighting added value.}}
In this research project, we will be using the CSEW and WMP datasets to investigate some of the environmental predictors of domestic abuse. First, using data from the CSEW, we will be looking at the association between neighbourhood-level characteristics, and the prevalence of domestic abuse as well the decision to report, and we will complement this with an additional analysis on WMP and census data. Previous literature has suggested various pathways of how neighbourhood characteristics affect domestic abuse, and our rich data allows us to determine the relative explanatory power of these. Understanding how neighbourhood-level characteristics affect the prevalence of domestic abuse and reporting behaviour is crucial for the most effective distribution of resources to help victims and targeted awareness campaigns. Second, we will be looking at how time-varying factors affect domestic abuse.

\textcolor{red}{\textit{What we know so far}} interestingly, there are no studies about this using UK data; neighbourhood-level predictors of domestic abuse: social disorganization theory (socio-economic disadvantage and residential instability disrupt social bonds a limit collective ability to maintain control and recognise IPV); cultural norms through social learning process (high IPV neighbourhoods where people observe influential others being rewarded for engaging in IPV, whereas in low IPV neighbourhoods perpetrators get socially ostracized); women's empowerment reduces IPV, especially financial independence;  abuser's lack of employment and alcohol consumption can be a risk factor; alcohol outlet density; churches, playgrounds, community networks might foster community cohesion and reduces IPV;  however, in deprived neighbourhoods, where IPV is accepted social interactions can increase IPV

\href{https://www.sciencedirect.com/science/article/abs/pii/S0277953616302891}{The relationship between electronic gaming machine accessibility and police-recorded domestic violence: A spatio-temporal analysis of 654 postcodes in Victoria, Australia, 2005–2014}

\href{https://journals.sagepub.com/doi/abs/10.1177/1525107115623938}{Economic Stress and Domestic Violence: Examining the Impact of Mortgage Foreclosures on Incidents Reported to the Police }

\href{https://journals.sagepub.com/doi/abs/10.1177/1524838013515758}{Neighborhood Environment and Intimate Partner Violence: A Systematic Review }
